gradient_analysis

### 2022-09-14 scripts/gradient_analysis.Rmd
move files

Indirect Grdient Analysis using PCA
explanation of how envfit actually works -> https://stackoverflow.com/questions/60953996/how-are-envfit-results-created 
```{r}
#sites ordinated by species abundances
#cor = F to use correlation matrix because variables are all on same scale
species_pca <- princomp(community_mat, cor = F)
plot(species_pca$scores, pch = 16)
summary(species_pca)
loadings(species_pca)
scores(species_pca)
biplot(species_pca)

>>>>

Indirect Grdient Analysis using PCA
explanation of how envfit actually works -> https://stackoverflow.com/questions/60953996/how-are-envfit-results-created 
```{r}
#sites ordinated by species abundances
#cor = F to use correlation matrix because variables are all on same scale
species_pca <- princomp(community_mat, cor = F)
#plot(species_pca$scores, pch = 16)
summary(species_pca)
#loadings(species_pca)
#scores(species_pca)
biplot(species_pca)
